Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-05 Paper.tex
Fixes from Vitalik.

@@

The address of the new contract is defined as being the leftmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In in the unlikely event that the addresses is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at, thus:

@@

where $\mathcal{S}$ is the SHA3 256-bit hash function, $\mathcal{R}$ is the RLP encoding function, $\mathcal{L}_y(X)$ evaluates to the leftmost $y$ bits of the binary data $X$ and $\mathbb{S}[x]$ is the address state of $x$ or $\varnothing$ if none exists.

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{equation}
\mathcal{P}(H, n) \leqslant \frac{2^{256}}{H_d}
\end{equation}

@@

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In in the unlikely event that the addresses is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at, thus:

@@

where $\mathcal{S}$ is the SHA3 256-bit hash function, $\mathcal{R}$ is the RLP encoding function, $\mathcal{L}_y(X)$ evaluates to the rightmost $y$ bits of the binary data $X$ and $\mathbb{S}[x]$ is the address state of $x$ or $\varnothing$ if none exists.

@@

This is a method for encoding arbitrarily structured binary data (byte arrays).

@@

The modified Merkle Patricia tree (trie) provides a persistent data structure to map between arbitrary-length binary data (byte arrays). It is defined in terms of a mutable data structure to map between 256-bit binary fragments and arbitrary-length binary data, typically implemented as a database.

@@

Hex-prefix encoding is an efficient method of encoding a arbitrary number of nibbles as a byte array. It is able to store an additional flag which, when used in the context of the trie (the only context in which it is used), disambiguates between node types.

@@

The state database is a mapping between SHA3-256 hashes (i.e. 256-bit binary fragments) and arbitrary byte data.

@@

The method of signing transactions is similar to the `Electrum style signatures'; it utilises the SECP-256k1 curve.

@@

The Low-level Lisp-like Language is a language created in order to efficiently author low-level programs (contracts) without having to resort to EVM-Assembly.

@@

The wire-protocol specifies a network-level protocol for how two peers can communicate. It includes handshake procedures and the means for transfering information such as blocks \& transactions
